FitBit Analysis

### 2023-02-15 02_paper/02_study/02_fitbit paper/FitBit_Plots_MK.Rmd
fitbit

df_heart_all <-
  read_rds(file = "final_data/heart_all.rds") |> 
  mutate(status = factor(status,
                         levels = c("Expert","Novice"),
                         labels = c("Expert","Novice")
                         )
         )

df_heart_min <-
  read_rds(file = "final_data/heart_min.rds")

df_heart_aggr <- 
  read_rds(file = "final_data/heart_aggr.rds") |> 
  mutate(status = factor(status,
                         levels = c("Novice","Expert"),
                         labels = c("Novice","Expert")
                         )
         )

@@

# merge demo data and fitbit data
df_anova <- merge(demo.data,
                  df_heart_aggr,
                  by="ID")

# clean variable names
df_anova <- df_anova %>% clean_names()

# check for outliers
outliers <-
  df_anova %>%
  group_by(type) %>%
  identify_outliers(mean)

# check for normality assumption --> can be checked by computing Shapiro-Wilk test for each time point. If the data is normally distributed, the p-value should be greater than 0.05
norm_assump <-
  df_anova %>%
  group_by(type) %>%
  shapiro_test(mean)

ggqqplot(df_anova, "mean", facet.by = "type")

# anova
res.aov <- rstatix::anova_test(data = df_anova,
                               dv = mean,
                               wid = id,
                               within = type)
get_anova_table(res.aov)

# anova expert novice
res.aov2 <- rstatix::anova_test(data = df_anova,
                               dv = mean,
                               between = status,
                               wid = id,
                               within = type)
get_anova_table(res.aov2)

# pairwise comparisons
pwc <- df_anova %>%
  pairwise_t_test(
    mean ~ type, paired = TRUE,
    p.adjust.method = "bonferroni"
    )
pwc

# Visualization: box plots with p-values
pwc <- 
  pwc %>% 
  add_xy_position(x = "type")

# boxplot
bxp_anova <- ggboxplot(data = df_anova, 
                 x = "type", 
                 y = "mean", 
                 add = "point")

bxp_anova + 
  stat_pvalue_manual(pwc) +
  labs(
    subtitle = get_test_label(res.aov, detailed = TRUE),
    caption = get_pwc_label(pwc)
    )

# saving plot 
ggsave(plot = bxp_anova,
       filename = "Plots/bxp_anova.svg",
       height = 5,
       width = 8,
       units = "in")

>>>>

df_heart_all <-
  read_rds(file = "data/heart_all.rds") |> 
  mutate(status = factor(status,
                         levels = c("Expert","Novice"),
                         labels = c("Expert","Novice")
                         )
         )

df_heart_min <-
  read_rds(file = "data/heart_min.rds")

df_heart_aggr <- 
  read_rds(file = "data/heart_aggr.rds") |> 
  mutate(status = factor(status,
                         levels = c("Novice","Expert"),
                         labels = c("Novice","Expert")
                         )
         )

@@

# disruption & confidence rating
df_rating <- 
  excel_sheets("data/Coding_SRI.xlsx") %>% 
  map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% # read in data with two sheets
  select(ID, # select relevant columns 
         disruption_factor, # -99 = subject did not notice event; -100 = experimenter did not asked for event
         confidence_factor,
         event
         ) %>% 
  mutate(disruption_factor = ifelse(disruption_factor < 0,
                                    yes = NA,
                                    no = disruption_factor
                                    ),
         confidence_factor = ifelse(confidence_factor < 0,
                                   yes = NA,
                                   no = confidence_factor),
         event = as_factor(event)
         ) %>% 
  na.omit() 
  # group_by(ID) %>% 
  # summarise("mean_disrup" = round(mean(disruption_factor), 2),
  #           "mean_confi" = round(mean(confidence_factor), 2))

# demographic data
df_demo <- 
  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% # read in excel 
  transmute(ID = LI06_05, # select and rename relevant columns 
            gender = factor(LI02_01_1,
                            levels = 1:2,
                            labels = c("male","female")
                            ),
            age = LI03_01, # 1 = male; 2 = female
            teaching_experience = LI04_01)

# merge two data frames by ID 
df_merge <- merge(df_demo,
                  df_rating,
                  by = "ID") %>% 
  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
                    "132")
         )

# rm(list = c("df_demo","df_rating"))

data_path <- "./data/heart_rate_data"

main <-
map(.x = dir(path = data_path,
             pattern = ".csv"),
    ~ read_csv(file.path(data_path, .), 
               id = "id",
               col_types = c("t","n")
               ) %>% 
  mutate(time = .$Time - min(.$Time),
         time = as.numeric(time),
         heart_rate = `Heart Rate`,
         ID = id,
         time_span = case_when(str_detect(string = id, pattern = "_a") ~ "after",
                               str_detect(string = id, pattern = "_m") ~ "main",
                               str_detect(string = id, pattern = "_p") ~ "pre",
                               str_detect(string = id, pattern = "_s") ~ "subsequent",
                               str_detect(string = id, pattern = "_i") ~ "interview",
                               TRUE ~ "overall"
                               ),
         ID = str_extract(string = ID,
                          pattern = "[:digit:]{3}"),
         ID = as.numeric(ID)
      ) %>%
      # filter(time <= 600) %>% # filter for 10min intervals
    filter(time <= 9000) %>% # filter for 2 hours 30min (maximal duration of study)
    select(!c("Time","Heart Rate","id"))
    ) %>%
  bind_rows()

main <-
  left_join(main, df_merge,
            by = "ID")

df_anova <-
  main %>% 
  filter(time_span != "overall") %>%   
  select("ID",
         "time_span",
         "heart_rate",
         "teaching_experience",
         "disruption_factor",
         "confidence_factor") %>% 
  mutate(time_span = fct_recode(time_span,
                                "Pre-Lehrphase" = "pre",
                                "Lehrphase" = "main",
                                "Post-Lehrphase" = "subsequent",
                                "Interviewphase" = "interview",
                                "Endphase" = "after"
                                ),
         time_span = factor(time_span,
                            levels = c("Pre-Lehrphase",
                                       "Lehrphase",
                                       "Post-Lehrphase",
                                       "Interviewphase",
                                       "Endphase"
                                       )
                            )
         ) %>%
  distinct() %>% 
  group_by(ID, time_span) %>%
  summarise(mean_hr = mean(heart_rate, na.rm = TRUE),
            mean_confi = mean(disruption_factor, na.rm = TRUE),
            mean_disrup = mean(disruption_factor, na.rm = TRUE),
            mean_te = mean(teaching_experience, na.rm = TRUE)
         )

# # merge demo data and fitbit data
# df_anova <- merge(df_anova,
#                   df_heart_aggr,
#                   by="ID")

# clean variable names
# df_anova <- df_anova %>% clean_names()

# Visualization
bxp <- ggboxplot(df_anova, x = "time_span", y = "mean_hr", add = "point")
bxp

# check for outliers
outliers <-
  df_anova %>%
  group_by(time_span) %>%
  identify_outliers(mean_hr)

# check for normality assumption --> can be checked by computing Shapiro-Wilk test for each time point. If the data is normally distributed, the p-value should be greater than 0.05
norm_assump <-
  df_anova %>%
  group_by(time_span) %>%
  shapiro_test(mean_hr)

# QQ plot draws the correlation between a given data and the normal distribution. 
plot <- 
  ggqqplot(df_anova, "mean_hr", facet.by = "time_span")

df_anova_subset <- subset(df_anova, select = c(time_span, mean_hr))

# # anova
# res.aov <- rstatix::anova_test(data = df_anova_subset,
#                                dv = mean_hr,
#                                wid = ,
#                                within = time_span)
# get_anova_table(res.aov)

# anova
df_anova_phase <- 
  aov(df_anova_subset$mean_hr~df_anova_subset$time_span)
summary(df_anova_phase)

# pairwise comparisons
pwc <- 
  pairwise.t.test(df_anova_subset$mean_hr, 
                  df_anova_subset$time_span, 
                  p.adjust="holm")

# effect size of ANOVA
install.packages("DescTools")
library(DescTools)
EtaSq(df_anova_phase)

effect_size_anova <-
  sqrt(0.3399757/(1-0.3399757))

# effect size of pairwise comparisons
library(dplyr)
library(rstatix)
df_anova_subset %>%
cohens_d(mean_hr~time_span) %>% 
as.data.frame()

# # pairwise comparisons
# pwc <- df_anova_subset %>%
#   pairwise_t_test(
#     mean_hr ~ time_span, paired = TRUE,
#     p.adjust.method = "bonferroni"
#     )
# pwc

# # Visualization: box plots with p-values
# pwc <- 
#   pwc %>% 
#   add_xy_position(x = "time_span")
# 
# # boxplot
# bxp_anova <- ggboxplot(data = df_anova, 
#                  x = "type", 
#                  y = "mean", 
#                  add = "point")
# 
# bxp_anova + 
#   stat_pvalue_manual(pwc) +
#   labs(
#     subtitle = get_test_label(res.aov, detailed = TRUE),
#     caption = get_pwc_label(pwc)
#     )

# # saving plot 
# ggsave(plot = bxp_anova,
#        filename = "Plots/bxp_anova.svg",
#        height = 5,
#        width = 8,
#        units = "in")

### 2023-02-15 02_paper/02_study/02_fitbit paper/Presentation_Analysis.Rmd
fitbit

>>>>

############## neuer Plot für GEBF #################

  plot_overall <-
  main %>% 
  filter(time_span == "overall") %>%
  select("ID","time_span", "time","heart_rate") %>% 
  distinct() %>% 
  ggplot(mapping = aes(x = time,
                       y = heart_rate
                       )
         ) +
  geom_smooth() +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
  scale_linetype_manual(values = c(1, 6)) +
  labs(x = "Zeit (in Sekunden)",
       y = "Herzrate (in Schlägen pro Minute)") +
  ggtitle("Gesamtverlauf der Herzrate in unterschiedlichen Phasen") +
  theme(text = element_text(family = "serif"),
        legend.text = element_text(size = 15),
        legend.title = element_blank(),
        axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 20),
        strip.text = element_text(size = 16),
        plot.title = element_text(size = 20, 
                                  face = "bold")) + 
    theme_apa() 
    # facet_grid(cols = vars(time_span),
    #          scales = "free_x")
